Hydrodynamic and particle dispersion modelling of floating solitary kelp:

### 2020-01-07 thesis_chapter_1.Rmd
added in new template for thesis. outputs updated for each chapter

---
title: "Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa:Development of a 3D spectral numerical coastal-flow model"
author: 
- RM Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    fig_caption: yes
    reference_docx: chapter_1_template.docx
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    theme:  simplex
bibliography: references.bib
---

>>>>

---
title: "Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa:Development of a 3D spectral numerical coastal-flow model"
author: 
- RM Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    theme:  simplex
bibliography: references.bib
---

### 2020-01-07 thesis_chapter_3.Rmd
added in new template for thesis. outputs updated for each chapter

---
title: 'Hydrodynamic and particle dispersion modelling of floating solitary kelp:
  An experimental approach'
author: "Ross Coppin"
date: "16/10/2019"
output:
  html_document:
    df_print: paged
---

>>>>

---
title: 'Hydrodynamic and particle dispersion modelling of floating solitary kelp:
  An experimental approach'
author: "Ross Coppin"
output:
  word_document:
    reference_docx: markdown/thesis_template.docx
  html_document:
    df_print: paged
  pdf_document:
    fig_caption: yes
bibliography: references.bib
---
